Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 intro.tex
intro and overview added citation

Current approaches to object class detection have reached a remarkable
level of performance in 2D bounding box
localization~\cite{pascal12,Felzenszwalb10,Girshick14}, due to their
ability to generalize across differences in object appearance,
lighting, and viewpoint. While this generalization
ability of these methods is benefitial for robustness, it also limits
the level of detail that these detectors can deliver as an output.

As a consequence, there has been increased interest in multi-view object
recognition, where viewpoint estimates are provided by
detectors in addition to 2D bounding boxes. Several attempts have been
made to estimate viewpoint along with object class detections,
implemented as extensions to existing detectors, such as the implicit
shape models~\cite{}, the constellation model~\cite{}, or the
deformable part model~\cite{Xiang12,Pepik12,Fidler12,Hejrati14}.

>>>>

Current approaches to object class detection have reached a remarkable
level of performance in 2D bounding box
localization~\cite{pascal12, Felzenszwalb10, Overfeat, Krizhevsky12, Girshick14}, due to their
ability to generalize across differences in object appearance,
lighting, and viewpoint. While this generalization
ability of these methods is benefitial for robustness, it also limits
the level of detail that these detectors can deliver as an output.

As a consequence, there has been increased interest in multi-view object
recognition, where viewpoint estimates are provided by
detectors in addition to 2D bounding boxes. Several attempts have been
made to estimate viewpoint along with object class detections,
implemented as extensions to existing detectors, such as the implicit
shape models~\cite{sun10eccv}, the constellation model~\cite{stark10bmvc}, or the
deformable part model~\cite{Felzenszwalb10, gu10eccv,Xiang12,Pepik12,Fidler12,Hejrati14}.
